---
title: "bayblade.pdf"
author: "Krishnan Raman"
date: "10/5/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Client (Arjun Raman) submitted experiment with 4 replicates upon 8 expermental units. The data document time in motion of an experimental unit:BayBlade. Client wishes to know if the Bayblades are significantly different, and the fastest/slowest bayblades.
The dataframe is shown below.

```{r}
bayblade<-read.csv("~/Desktop/514/bayblade.csv", sep=",", header=T)
bayblade
m<-as.matrix(bayblade)
sapply( 1:8, function(x) { mean(m[,x]) })
```
Lets fit a linear model with 8 factors & perform Analysis of Variance.
```{r}
alldata<- c(m[,1],m[,2],m[,3],m[,4],m[,5],m[,6],m[,7],m[,8]) 
groups<- c(rep(1,4),rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4),rep(7,4),rep(8,4))
model<-lm(alldata~as.factor(groups))
summary(model)
plot(model)
```
An analysis of variance is given below:
```{r}
anova(model)
```

Conclusion: The p-value 1.6e-14 is highly significant, indicating at a 5% level, the bayblades are significantly different from each other. The F test has a score of 71 >> 1, confirming the difference of the means.
The fastest bayblade is group1 ( pg) with mean time: 79.25
The slowest bayblade is group3 ( gr) with mean time: 79.25 - 58.5 = 20.75

The Order statistics are:
gr < y < p < b < yo < gg < o < pg
